IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/real.tex
init of cowl

\subsubsection{Client-side embedding: Gecko}
\Red{HERE}

We remark that this is similar to the existing
\texttt{postMessage} API used for iframe and worker
communications~\cite{webworkers}.
%
Thus, the COWL implementation provides an IFC version of
\texttt{postMessage}, defined in terms of |send|, that additionally
takes a label argument.

%
In turn, each task created with |sandbox| is
executed in a separate thread, running a separate, \emph{fresh} instance of our
modified JS runtime.
%
Formally, |sandbox| is defined with |klone(tS) =
tS0|, where |tS0| is the global object corresponding to the standard
JS library (e.g., |tS0| contains \texttt{Object}, \texttt{Array},
etc.).

Unsurprisingly, our coarse-grained combined language approach has been
inspired by existing browser (security) architectures.
%
Browsers, for example, isolate pages of different origins by running
them in separate runtimes.
%
Similarly, they provide the worker JS object~\cite{webworkers}, which allows
JavaScript to execute code in separate threads with separate JS
runtimes (and fresh global objects).
%
In both cases, code relies on the \texttt{postMessage} message-passing
API for communication, similar to our system.\footnote{
  The message-passing approach is, in part, due to ECMAScript's lack
  of well-defined semantics for concurrency.
  %
  Hence sharing and accessing objects such as the DOM across worker
  threads is undefined.
}
%
As suggested by our formal semantics, COWL can directly leverage these
mechanisms to implement the semantics of |specLangJS roundrobinf|
without modifying the JS runtime or intrusively changing the browser
layout engine.

>>>>

\subsubsection{Client-side embedding: Gecko}

We now describe some of the implementation aspects of
COWL~\cite{swapi}, for which this work serves as the theoretical
underpinning.
%
Since the architecture of COWL is similar to that of Node.js, we focus
on the main differences.

Most notably, tasks in COWL usually correspond to browsing contexts,
such as iframes.
%
Hence, the global object |tS0| also contains the DOM, the
\verb|XMLHttpRequest| (XHR) object, etc.
%
To ensure that JavaScript code cannot communicate using these objects
(e.g., to the network with XHR or persistent storage using the DOM),
COWL additionally uses content security policy (CSP)~\cite{csp1.1}.\footnote{
  Since CSP does not yet address message passing or navigation, this
  was addressed explicitly.
}
%
Note, that this does not prevent tasks from manipulating the DOM
(e.g., to render information).
%
Rather, to enforce task-isolation, external effects due to DOM access
are suppressed.
